\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{hyperref}
\usepackage{helvet}
\usepackage{fontenc}
\usepackage{keycommand}
\usepackage{xstring}

\geometry{a4paper, top=1.5cm, bottom=1.5cm, left=2cm, right=2cm}
\pagestyle{empty}
\renewcommand{\familydefault}{\sfdefault}

\begin{document}

\begin{center}
    \textbf{\Large Erik Newland} \\
    \vspace{0.2cm}
    7608611002 \hspace{0.2cm} | \hspace{0.2cm} eriknewland93@gmail.com \hspace{0.2cm} | \hspace{0.2cm} "https://www.linkedin.com/in/erik-newland/" \hspace{0.2cm} | \hspace{0.2cm} "https://github.com/eriknewland" \hspace{0.2cm} | \hspace{0.2cm} "https://eriknewland.netlify.app/"
\end{center}

\textbf{\large Summary} \\
Self-taught full-stack software engineer with a passion for learning new technologies and creatively solving problems.

\textbf{\large Skills} \\
\begin{itemize}[noitemsep,topsep=0pt]
    \item MongoDB (Advanced)
    \item Firebase (Advanced)
    \item JavaScript (Advanced)
    \item TypeScript (Intermediate)
    \item Python (Intermediate)
    \item HTML (Advanced)
    \item CSS (Advanced)
    \item Node.js (Advanced)
    \item Next.js (Advanced)
    \item React (Advanced)
    \item Express (Advanced)
    \item React Native (Intermediate)
    \item SQL (Intermediate)
    \item AWS (Intermediate)
    \item Docker (Intermediate)
    \item Git (Intermediate)
\end{itemize}

\textbf{\large Experience} \\
\textbf{Sindolor} \hfill Operations Manager \hfill June 2017 - December 2021 \\
Designed and managed cannabinoid-based medical trials with a success rate of 70\%. Developed and secured a patent for a novel cannabinoid-based treatment for opioid addiction.

\textbf{Flux} \hfill Product Manager \hfill October 2018 - July 2019 \\
Enhanced projected yields by over 30\% through hardware redesign and improved genetics sourcing. Developed product specifications, presented to investors and shareholders, and collaborated with strategic partners, leading to multiple investment rounds.

\textbf{Plebnet} \hfill Volunteer Software Engineer/Community Manager \hfill April 2023 - August 2023 \\
Implemented new payment rails, redesigned routes and infographics, and conducted end-to-end testing using Next.js, React, and Astro frameworks. Streamlined deployment to Vercel \& Fly.io, created Docker images and containers, and rewrote a JavaScript Telegram bot in Python, enhancing overall project efficiency and functionality. Participated in code reviews, architecture discussions, UX/UI discussions, and mentored less experienced programmers.

\textbf{\large Projects} \\
\textbf{SunChip API} \hfill 2 weeks \\
Implemented two-layer authentication and utilized PostgresQL and Sequelize to ensure data security and longevity of the system architecture. Scaled an archaic back-end to 20x VU traffic with a sub 1\% error rate and load times under 50ms. Created a suite of custom tools (csvtransformers) to help the team extract and transform data, speeding up our service by 25-50ms on any given query.

\textbf{SpreadShot} \hfill 4 weeks \\
Developed a SAAS website that combines job scraping via puppeteer with openAI's API to provide users with a list of jobs (relevant to user search) and cover letters/resumes to increase job application throughput by 10x.

\textbf{\large Activities} \\
\textbf{World of Warcraft} \hfill 5 years \\
Competitive World of Warcraft player in high school, achieving a ranking of Top 10 U.S. and top 25 World during my peak.

\textbf{\large Education} \\
\textbf{University of California, Santa Barbara} \hfill Bachelor of Arts \hfill September 2011 - June 2016 \\
\textbf{Hack Reactor} \hfill Advanced Software Immersive Bootcamp \hfill December 2022 - March 2023

\textbf{\large References} \\
John Rhoads, Manager, john@vergestrat.com, 123456879

\end{document}